Examining background gene lists using simulation - comparison of different enrichment techniques

### 2024-06-08 analysis/sim/run_simpw.Rmd
update
update sim

SIMS=500
FRAC_DE=0.05
FC=1
N_REPS=5
DGE_FUNC="deseq2"
SUM_COUNT=2e7
VARIANCE=c(0.3,0.325,0.35,0.375,0.4,0.425,0.45)

@@

## Plot

@@

par(mfrow=c(1,3))

@@

par(mfrow=c(1,1))

>>>>

SIMS=500
#run 500 sims
FRAC_DE=0.05
FC=1
N_REPS=3
DGE_FUNC="deseq2"
SUM_COUNT=2e7
VARIANCE=c(0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1,1.1,1.2,1.3,1.4,1.5)

@@

## Plotfig1_ORAjac.png

@@

par(mfrow=c(1,3))
par(mar=c(c(5.1, 5.1, 2.1, 2.1) ))

@@

png("fig3_sim.png",width=720, height=480)
par(mar=c(c(5.1, 5.1, 2.1, 2.1) ))
par(mfrow=c(1,3))

dev.off()
